---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(orextdb)
```

# orextdb

The `{orextdb}` package interfaces with the Oregon Extended Assessment (ORExt) API which pulls from the live ORExt database to simplify access to the data. This package is primarily used in conjunction with `{dbprocess}` & `{exirt}`. This vignette explains the main functions in `{orext}` to help someone building out the aforementioned packages, or directly pulling data for another reason.  The goal of `{orext}` is to make data extraction into R easy.  


<!-- badges: start -->
[![R-CMD-check](https://github.com/UO-BRT/orextdb/workflows/R-CMD-check/badge.svg)](https://github.com/UO-BRT/orextdb/actions)
[![Codecov test coverage](https://codecov.io/gh/UO-BRT/orextdb/branch/main/graph/badge.svg)](https://app.codecov.io/gh/UO-BRT/orextdb?branch=main)
<!-- badges: end -->

## Accessing the Data Base

You can check if you have access with `db_key()`. If this returns an empty string, you do not have the key. You can set the key by wrapping the key in quotes within `db_set_key()` (e.g., `db_set_key('asdfjkl-123456')`)

Databases are specified with the prefix "ORExt" and then the final two digits of the academic year. So for 2018-19, we specify `db = 'ORExt1819'`. 

We also have to specify which table we want. If we want to estimate the ability estimates, we need to specify which table we want pulled from the database. 

This is done with the argument `table = `, which is a string specifying the specific table from the Oregon Extended live database. 

`table` should be one of 

    * "Accomodations"
    * "Answers"
    * "Districts" 
    * "Exams"
    * "Items" 
    * "Preferences" 
    * "Schools"
    * "Students" 
    * "Students_old" 
    * "Submissions" 
    * "SupplementalDistricts"
    * "SupplementalSchools"
    * "Tasks"
    * "User" 
    * "UserStudents"
    * "UserStudents_old"


Check the documentation with `?db_get()` for further arguments, though defaults have been set to be useful and will not need to be changed typically.

# Load the library

As with any package, we need to load the library. If you do not have the package installed, you can use `remotes::install_github('UO-BRT/orextdb')` before this step, assuming you have access to the repository. 

```{r setup}
library(orextdb)
```

# Check current data base

We can see the current database and the general formatting of database names with this call. 

```{r}
current_db()
```

## internal workings of `current_db()`

This function is used internally if the user does not specify a specific database, so this is the database the package assumes if unspecified. The current database switches from [current year - 1, current year] to [current year, year + 1] after September 1st. For example: calling `current_db()` on August 31, 2022 returns `ORExt2122`, and calling it on September 1, 2022 returns `ORExt2223`. With additional functionality in the API, new functions will be added to list all available databases.

## check formatting of database name

As you can see, databases are formatted with the prefix `ORExt` followed by the academic year. Academic year is specified as the last two digits of each year in the academic year (e.g., 2018-2019 = `1819`, 2019-2020 = `1920`, etc.). Hence, the database for the 2018-2019 OR Extended Assessment is `ORExt1819`. If you are not sure if you've specified this correctly, you can check with `check_db()`. This function will also give you a message about how to fix your code, if you formatted this incorrectly.

```{r}
check_db('1819', verbose = TRUE)
```

# Retreive table from database

Retreiving a given table from the database is simple. Calling `db_get()`, we can access any of the following tables with the `table` argument:

* Accomodations
* Answers
* Districts
* Exams
* Items
* Preferences
* Schools
* Students
* Students_old
* Submissions
* SupplementalDistricts
* SupplementalSchools
* Tasks
* User
* UserStudents
* UserStudents_old

The `table` argument is required and cannot be left blank. If you do not specify the database (i.e., `db` in `db_get()`) it defaults to the output of `db_current()`. 

This is how you can access the Items table for the 2018-2019 academic year, for example:

```{r}
db_get(table = 'Items')
```

If we wanted to access the ids for various schools, we could do that with the same function, but modifying `table`. Column names default to `snake_case`. If you prefer `camelCase` names, you can access these with `raw = TRUE`, indicating you want the unformatted (i.e., raw) column names.

```{r}
db_get(table = 'Schools', db = 'ORExt2021', raw = TRUE)
```


This package is meant to be used in conjunction with two other packages, please see [`{exirt}`](https://github.com/UO-BRT/exirt) for an explanation of the three-package pipeline.
