---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
library(orextdb)
```

# orextdb

<!-- badges: start -->
[![R-CMD-check](https://github.com/UO-BRT/orextdb/workflows/R-CMD-check/badge.svg)](https://github.com/UO-BRT/orextdb/actions)
<!-- badges: end -->

The goal of **orextdb** is to make data extraction into R easy.  

## Installation

``` r
# install.packages("remotes") # if not previously installed
remotes::install_github("UO-BRT/orextdb")
```

## Keys
You first need to make sure you have a key to access the web API housing the data. The **orextdb** package includes helper functions for working with your key. First, store your key in your `.Renviron` using the following code, swapping the text for your specific key.

```{r eval = FALSE}
library(orextdb)
db_set_key(key = "mykeyabcdefg")
```

This will write a key to your `.Renviron` that is accessible via `db_key()`. You should only need to do this once, and you will need to make sure you restart your R session for the change to take effect. Generally, you won't need to access your key, but if for any reason you do, you can always run `db_key()` and your key will be printed to the console.

## Accessing data
Once you've set your key, you can access any of the tables in the Oregon Extended Database via `db_get()`. Just supply the name of the table you want, and it will be returned. If you don't know the name of the table you want, you can provide any text you want and the available tables will be printed for you.

```{r error = TRUE}
db_get("hardyharhar")
```

Eventually, functions will be built that combine tables in more useful formats, but currently it just returns the tables in their raw form.
